---
title: "week9"
author: "huiyingmiao"
date: "June 5, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 11 DATA IMPORT
```{r}
library(tidyverse)
```
```{r}
read_csv("The first line of metadata
  The second line of metadata
  x,y,z
  1,2,3",skip=2)
```
```{r}
read_csv("#the comment i want to skip
         x,y,z
         1,2,3",comment="#")
```
```{r}
read_csv("1,2,3\n 4,5,6",col_names = FALSE)
```
```{r}
read_csv("1,2,3\n 4,5,6",col_names =c( "X","Y","Z"))# a vector as name--c()
```

```{r}
read_csv("a,b,c\n n1,n2,.", na =".") #na should be low case~
```

## 11.2.2 Exercises
### 1 What function would you use to read a file where fields were separated with
“|”?
```{r}
read_delim("a|b\n1.0|2.0", delim = "|")
```
## 2 Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?

read_csv(file, **col_names = TRUE**, **col_types = NULL**,
  **locale = default_locale()**, **na = c("", "NA")**, **quoted_na = TRUE**,
  **quote = "\""**, comment = "", **trim_ws = TRUE**, skip = 0, **n_max = Inf**,
  **guess_max = min(1000, n_max)**, **progress = show_progress()**)
  
read_tsv(file, col_names = TRUE, col_types = NULL,
  locale = default_locale(), na = c("", "NA"), quoted_na = TRUE,
  quote = "\"", comment = "", trim_ws = TRUE, skip = 0, n_max = Inf,
  guess_max = min(1000, n_max), progress = show_progress())

## 3 What are the most important arguments to read_fwf()?

read_fwf(file, **col_positions**, col_types = NULL, locale = default_locale(),
  na = c("", "NA"), comment = "", skip = 0, n_max = Inf,
  guess_max = min(n_max, 1000), progress = show_progress())
  
## 4 Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you’ll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame?

"x,y\n1,'a,b'"

```{r}
read_csv("x,y\n1,'a,b'",quote="'")
```
## 5 Identify what is wrong with each of the following inline CSV files. What happens when you run the code?

```{r}
read_csv("a,b\n1,2,3\n4,5,6")#one colume is dropped.
```

```{r}
read_csv("a,b,c\n1,2\n1,2,3,4")#numbers of columes and that in the header don't match.
```

```{r}
read_csv("a,b\n\"1")# quote? I dont know...
```


```{r}
read_csv("a,b\n1,2\na,b")# what do you want to say?
```
```{r}
read_csv("a;b\n1;3")# delim=";"
```

```{r}
read_delim("a;b\n1;3",delim  = ";")
```

============================
```{r}
str(parse_integer(c("1", "2", "3")))
str(parse_logical(c("TRUE", "FALSE", "NA")))
str(parse_date(c("2010-01-01", "1979-10-14")))
```

```{r}
parse_integer(c("1", "231", ".", "456"),na=".")
```

```{r}
x<-parse_integer(c("123", "345", "abc", "123.45"))
x

```
```{r}
problems(x)
```

**11.3.1 Numbers**
```{r}
parse_double("1,23",locale = locale(decimal_mark = ","))#You can override the default value of . by creating a new locale and setting the decimal_mark argument.
```

```{r}
parse_number("$100")#it ignores non-numeric characters before and after the number. 
```
```{r}
parse_number("123,456,789")
parse_number("123.456.789")
parse_number("123.456.789",locale = locale(grouping_mark = "."))#combination of parse_number() and the locale
```

**11.3.2 Strings**

we can get at the underlying representation of a string using charToRaw():
```{r}
charToRaw("hadley")
```

```{r}
x2 <- "\x82\xb1\x82\xf1\x82\xc9\x82\xbf\x82\xcd"#The first argument to guess_encoding() can either be a path to a file, or, as in this case, a raw vector (useful if the strings are already in R).
guess_encoding(charToRaw(x2))
```
**11.3.4 Dates, date-times, and times**
```{r}
parse_datetime("2010-10-10T2009")#there's a Capital T.
parse_datetime("2010-10-10")#If time is omitted, it will be set to midnight
parse_datetime("20101010")
```
```{r}
parse_date("2010/10/10")#expects a four digit year, a - or /, the month, a - or /, then the day.
```

```{r}
library(hms)
parse_time("10:10 am")
parse_time("10:10 pm")
```

## 11.3.5 Exercises

### 1. What are the most important arguments to locale()?

locale(date_names = "en", date_format = "%AD", time_format = "%AT",
  decimal_mark = ".", grouping_mark = ",", tz = "UTC",
  encoding = "UTF-8", asciify = FALSE)

### 2. What happens if you try and set decimal_mark and grouping_mark to the same character? What happens to the default value of grouping_mark when you set decimal_mark to “,”? What happens to the default value of decimal_mark when you set the grouping_mark to “.”?

if set decimal_mark and grouping_mark to the same character, it will return Error: `decimal_mark` and `grouping_mark` must be different.

parse_number("123,456.789", locale = locale(decimal_mark = ".",grouping_mark = "."))
```
when you set decimal_mark to “,”, grouping_mark is set to a period.
```{r}
parse_number("12.34,56", locale = locale(decimal_mark = ","))
```
when you set the grouping_mark to “.”,decimal_mark is set to a comma.
```{r}
parse_number("12.34,56", locale = locale(grouping_mark = "."))
```

```{r}
locale(decimal_mark = ",")
 locale(grouping_mark = ".")
```

### 3. I didn’t discuss the date_format and time_format options to locale(). What do they do? Construct an example that shows when they might be useful.


```{r}
parse_date("1 janvier 2015", "%d %B %Y", locale = locale("fr"))
```

### 4. If you live outside the US, create a new locale object that encapsulates the settings for the types of file you read most commonly.

???

### 5. What’s the difference between read_csv() and read_csv2()?

read_csv, comma delimited files;   
read_csv2, semicolon seperated files.


### 6.What are the most common encodings used in Europe? What are the most common encodings used in Asia? Do some googling to find out.

see in wikipedia...

### 7. Generate the correct format string to parse each of the following dates and times:

d1 <- "January 1, 2010"
d2 <- "2015-Mar-07"
d3 <- "06-Jun-2017"
d4 <- c("August 19 (2015)", "July 1 (2015)")
d5 <- "12/30/14" # Dec 30, 2014
t1 <- "1705"
t2 <- "11:15:10.12 PM"
```{r}
d1 <- "January 1, 2010"
d2 <- "2015-Mar-07"
d3 <- "06-Jun-2017"
d4 <- c("August 19 (2015)", "July 1 (2015)")
d5 <- "12/30/14" # Dec 30, 2014
t1 <- "1705"
t2 <- "11:15:10.12 PM"
parse_date(d1, "%B %d, %Y")
parse_date(d2,"%Y-%b-%d")
parse_date(d3,"%d-%b-%Y")
parse_date(d4,"%B %d (%Y)")
parse_date(d5,"%m/%d/%y")
parse_time(t1,"%H%M")
parse_time(t2,"%I:%M:%OS %p")
```

