---
title: "week8"
author: "huiyingmiao"
date: "May 30, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(ggplot2)
```

#7 go on
```{r}
ggplot(data=faithful)+
  geom_point(mapping=aes(x=eruptions,y=waiting))
```
```{r}
ggplot(data = faithful, mapping = aes(x = eruptions)) + 
  geom_freqpoly(binwidth = 0.25)
```
```{r}
ggplot(faithful,aes(eruptions))+
  geom_freqpoly(binwidth=0.25)
```
the later is more concisely~

```{r}
library(tidyverse)
diamonds%>%
  count(cut,clarity)%>%
  ggplot(aes(clarity,cut,fill=n))+
  geom_tile()
```

# 10 Tibbles

```{r}
library(tidyverse)
```

**coerce a data frame to a tibble**
```{r}
as_tibble(iris)
```
**create a tibble**
```{r}
tibble(
  x=1:5,
  y=1,
  z=x^2+y
)
```
**tibble never converts strings to factors!**

**To refer to non-syntactic names(not start with a letter), you need to surround them with backticks, `:**


```{r}
tb<-tibble(
`:)`="smile",
` `="space",
`2000`="number"
)
tb
```

** tribble(), short for transposed tibble.they start with ~, and entries are separated by commas.**
```{r}
tribble(
  ~x,~y,~z,
  #---/---
  "a",1,2,
  "b",3,4
)
```

#####tibble vs data frame

```{r}
ttb<-tibble(
  a=1:12,
  b=a^3+6,
  c=log(a),
  d=2.2,
  e=a*b-c+d,
  f=1,
  g=6,
  h=2,
  i=1,
  j=66,
  k=11,
  l=66
)
ttb%>%
  print(n=12,width=Inf) #why don't output 12 rows....
```
```{r}
ttb
```
```{r}
class(ttb)
```

** pull out a single variable.**
**$ and [[. [[ can extract by name or position; $ only extracts by name but is a little less typing.**

```{r}
#extract by name
ttb$a
ttb[["a"]]
#extract by position
ttb[[2]]
```
```{r}
class(as_data_frame(ttb))
```

##10.5 Exercises

### 1 How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).
```{r}
mtcars 
```

```{r}
class(mtcars)# tibble has "tbl_df"     "tbl"    
```
```{r}
class(as_tibble(mtcars))
```


### 2 Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?

**tibbles are more strict: they never do partial matching**

```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x #partial matching
df[, "xyz"] # returns a vector, rather than a data frame

df[, c("abc", "xyz")]
```







```{r}
tbdf<-as_tibble(df)
tbdf$x
tbdf[, "xyz"]
tbdf[, c("abc", "xyz")]
```
### 3 If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?

use var[["mpg"]] or var$mpg

### 4 Practice referring to non-syntactic names in the following data frame by:

1 Extracting the variable called 1.

2 Plotting a scatterplot of 1 vs 2.

3 Creating a new column called 3 which is 2 divided by 1.

4 Renaming the columns to one, two and three.

```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
#extract variable 1
annoying[["1"]]
annoying$`2`
#plot
ggplot(annoying, aes(x=`1`, y=`2`))+
  geom_point()

annoying%>%
  mutate(`3`=`2`/`1`)
#creat a new colunm
annoying[["3"]]<-annoying[["2"]]/annoying[["1"]]
#rename the columns
annoying<-rename(annoying,one=`1`,two=`2`,three=`3`)
annoying
 

```

### 5 What does tibble::enframe() do? When might you use it?
*enframe() converts named atomic vectors or lists to two-column data frames. For unnamed vectors, the natural sequence is used as name column.*

*deframe() converts two-column data frames to a named vector or list, using the first column as name and the second column as value.*

```{r}
tibble::enframe(c(x=1,y=2,h=3)) #named vector
tibble::enframe(c(1,6,3)) #unamed vector
```

### 6 What option controls how many additional column names are printed at the footer of a tibble?
print.tbl_df

print(x, ..., n = NULL, width = NULL, n_extra = NULL)

