---
title: "assignment 5"
author: "huiyingmiao"
date: "May 8, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(nycflights13)
library(tidyverse)
```



```{r}
nycflights13::flights
```

```{r}
nov_dec <- filter(flights, month %in% c(11, 12))
nov_dec
```

##5.2.4 Exercises  

### 1.Find all flights that  

1) Had an arrival delay of two or more hours  
```{r}
filter(flights, arr_delay >= 120 )
```

2) Flew to Houston (IAH or HOU)  
```{r}
filter(flights,dest== "IAH" | dest=="HOU" )
```

3) Were operated by United, American, or Delta  
```{r}
filter(flights,carrier== "UA" | carrier== "AA"|carrier== "DL")
```

4) Departed in summer (July, August, and September)  
```{r}
filter(flights,month== "8" | month== "7" | month== "9")
```

```{r}
filter(flights,month %in% c(7,8, 9))
```

5)Arrived more than two hours late, but didn’t leave late

```{r}
filter(flights,arr_delay>120 & dep_delay<=0)
```

6) Were delayed by at least an hour, but made up over 30 minutes in flight  
```{r}
filter(flights,arr_delay>=120 & dep_delay-arr_delay>30)
```

7)Departed between midnight and 6am (inclusive)

```{r}
filter(flights,dep_time<=600 | dep_time==2400)
```

### 2 Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?

between(x, left, right): a shortcut for x >= left & x <= right

For Departed in summer (July, August, and September)  
```{r}
filter(flights,between(month, 7, 9))
```

### 3 How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r}
filter(flights, is.na(dep_time))
```


### 4 Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)

```{r}
NA ^ 0
NA | TRUE
FALSE & NA
NA & TRUE
FALSE | NA
NA * 0 
```

NA ^ 0 == 1   
NA | TRUE is TRUE  
anything and FALSE is  FALSE  
_FALSE | NA==NA_

## 5.3.1 Exercises

###1 How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).  


```{r}
arrange(flights,desc(is.na(dep_time)),dep_time)
```

### 2. Sort flights to find the most delayed flights. Find the flights that left earliest.

```{r}
arrange(flights, desc(dep_delay))
arrange(flights,dep_delay)
```

By default, sorting is ASCENDING

### 3. Sort flights to find the fastest flights.
```{r}
arrange(flights,air_time)
```

### 4. Which flights travelled the longest? Which travelled the shortest?
```{r}
arrange(flights,desc(distance))
arrange(flights,distance)
```

Longest:flight 51, 4983  
Shortest:flight 3833,80

## 5.4.1 Exercises

### 1.Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.

```{r}
select(flights,dep_time,dep_delay,arr_time,arr_delay)
select(flights,starts_with("dep"),starts_with("arr"))
```

### 2.What happens if you include the name of a variable multiple times in a select() call?

```{r}
select(flights, dep_time,dep_time, arr_time,arr_delay,dep_time)
```

duplications are ignored.

### 3.What does the one_of() function do? Why might it be helpful in conjunction with this vector?

one_of(): variables in character vector.
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, one_of(vars))

select(flights, one_of("year", "month", "day", "dep_delay", "arr_delay"))
```


### 4.Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?


```{r}
select(flights, contains("TIME"))
```

Case is ignored...


# 5. mutate

```{r}
flights_sml <- select(flights, 
  distance, 
  air_time
)
mutate(flights_sml,
  speed = distance / air_time * 60
)
mutate(flights_sml,
  hours = air_time / 60,
  gain_per_hour = 100 / hours
)
transmute(flights,
  
  hours = air_time / 60,
  gain_per_hour = 100 / hours
)
```

## 5.5.2 Exercises

###1.Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
dep_flights<-select(flights,dep_time)
sched_flights<-select(flights,sched_dep_time)
mutate(dep_flights,dep_time_min=dep_time%/%100*60+dep_time%%100)
mutate(sched_flights,sched_dep_time_min=sched_dep_time%/%100*60+sched_dep_time%%100)
```


###2.Compare air_time with arr_time - dep_time. What do you expect to see? What do you see? What do you need to do to fix it?

```{r}
compare<-select(flights,dest,arr_time,dep_time,air_time)
compare2<-mutate(compare,air_time2=arr_time-dep_time)
transmute(compare2,dest,arr_time,dep_time,air_time,air_time_compare=air_time2%/%100*60+air_time2%%100
)
```

###3.Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?

dep_time - sched_dep_time = dep_delay

```{r}
flights2<-select(flights,dep_time,sched_dep_time,dep_delay)
mutate(flights2,dep_delay2=dep_time - sched_dep_time)
```

###4.Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for min_rank().

```{r}
flights2<-mutate(flights,dep_delay_rank=min_rank(-dep_delay))
  filter(flights2,dep_delay_rank<=10)
```

###5.What does 1:3 + 1:10 return? Why?

```{r}
1:3+1:10
```

the shorter vector’s values to get vectors of the same length.

###6.What trigonometric functions does R provide?

These functions give the obvious trigonometric functions. They respectively compute the cosine, sine, tangent, arc-cosine, arc-sine, arc-tangent, and the two-argument arc-tangent.

cos(x)
sin(x)
tan(x)

acos(x)
asin(x)
atan(x)
atan2(y, x)

cospi(x)
sinpi(x)
tanpi(x)