---
title: "week 7"
author: "huiyingmiao"
date: "May 22, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
ggplot(data = diamonds) +
  geom_histogram(mapping = aes(x = x), binwidth = 0.1)

diamonds %>% 
  count(cut_width(x, 0.5))
```

## 7.3.4 Exercises

### 1 Explore the distribution of each of the x, y, and z variables in diamonds. What do you learn? Think about a diamond and how you might decide which dimension is the length, width, and depth.

I cannot tell which dimension is length...without documentatioin   
x:length in mm (0–10.74);y:width in mm (0–58.9);z:depth in mm (0–31.8)



```{r}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = x))

diamonds %>% 
  count(x)

diamonds %>% 
  filter(x < 3.75)  %>%
  count(x)



smaller <- diamonds %>% 
  filter(x < 4) 
ggplot(data = smaller, mapping = aes(x = x)) +
  geom_histogram(binwidth = 0.1)

ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = x), binwidth = 0.5) +
  coord_cartesian(ylim = c(0, 50))
```

```{r}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = y))

ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y), binwidth = 0.5) +
  coord_cartesian(xlim = c(0, 10))
```

```{r}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = z))

ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = z), binwidth = 0.5) +
  coord_cartesian(xlim = c(0, 10))
```



### 2 Explore the distribution of price. Do you discover anything unusual or surprising? (Hint: Carefully think about the binwidth and make sure you try a wide range of values.)

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = price), binwidth = 1)+ 
coord_cartesian(ylim = c(0, 10))

ggplot( filter(diamonds,  price> 10000)) + 
  geom_histogram(mapping = aes(x = price), binwidth = 1) +
  coord_cartesian(ylim = c(0, 10))
```
```{r}
diamonds %>%
  
  count(price>=17500)
```


### 3 How many diamonds are 0.99 carat? How many are 1 carat? What do you think is the cause of the difference?

```{r}
diamonds %>% 
  filter(carat>=0.99 & carat<=1)%>%
  count(carat)


diamonds %>% 
  filter(carat>=0.9 & carat<=1.1)%>%
  count(carat)
```
No big difference in price between 1 and 0.99...Maybe 1carat sounds good? or means more reward?



### 4 Compare and contrast coord_cartesian() vs xlim() or ylim() when zooming in on a histogram. What happens if you leave binwidth unset? What happens if you try and zoom so only half a bar shows?

xlim(ylim)will remove non-finite values.
```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = price), binwidth = 1) +
  coord_cartesian(xlim = c(10000, 11000),ylim = c(0, 5))
```

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = price), binwidth = 1) +
 xlim (10000, 11000) +
 ylim (0, 5)
```

with or without binwidth

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = price),binwidth = 1) +
 xlim (100, 11000) +
 ylim (0, 500)
```

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = price)) +
 xlim (100, 11000) +
 ylim (0, 500)
```

## 7.4.1 Exercises

### 1 What happens to missing values in a histogram? What happens to missing values in a bar chart? Why is there a difference?

missing values are dropped in histogram,AND are a category in bar chart.   
In a histogram, the x aesthetic variable needs to be numeric, and stat_bin groups the observations by ranges into bins. Since the numeric value of the NA observations is unknown, they cannot be placed in a particular bin, and are dropped.

```{r}
diamonds2 <- diamonds %>% 
  mutate(y = ifelse(y < 3 | y > 20, NA, y))
ggplot(diamonds2,aes(x = y)) +
  geom_histogram()
```

```{r}
diamonds2 <- diamonds %>% 
  mutate(y = ifelse(y < 3 | y > 20, NA, y))
ggplot(diamonds2,aes(x = y)) +
  geom_bar()
```


### 2 What does na.rm = TRUE do in mean() and sum()?

remove NA before calculating
```{r}
mean(c(0, 1, 2, NA), na.rm = TRUE)

sum(c(0, 1, 2, NA), na.rm = TRUE)

```

## 7.5
```{r}
ggplot(data = diamonds, mapping = aes(x = price)) + 
  geom_freqpoly(mapping = aes(colour = cut), binwidth = 100)
```
```{r}
ggplot(data = diamonds, mapping = aes(x = price, y = ..density..)) + 
  geom_freqpoly(mapping = aes(colour = cut), binwidth = 500)
```

```{r}
ggplot(data = diamonds, mapping = aes(x = cut, y = price)) +
  geom_boxplot()
```
```{r}
ggplot(data = diamonds, mapping = aes(x = cut, y = price)) +
  geom_point(size=0.1)
```


### 7.5.1.1 Exercises

### 1 Use what you’ve learned to improve the visualisation of the departure times of cancelled vs. non-cancelled flights.

```{r}
nycflights13::flights %>% 
  mutate(
    cancelled = is.na(dep_time),
    sched_hour = sched_dep_time %/% 100,
    sched_min = sched_dep_time %% 100,
    sched_dep_time = sched_hour + sched_min / 60
  ) %>% 
  ggplot() +
    geom_boxplot(mapping = aes(y = sched_dep_time, x = cancelled))
```


### 2 What variable in the diamonds dataset is most important for predicting the price of a diamond? How is that variable correlated with cut? Why does the combination of those two relationships lead to lower quality diamonds being more expensive?

carat? lower quality diamonds are bigger?
```{r}
ggplot(data = diamonds, mapping = aes(x = cut, y = carat)) +
  geom_boxplot()
```


### 3 Install the ggstance package, and create a horizontal boxplot. How does this compare to using coord_flip()?

install.packages("ggstance")
library("ggstance")


```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = reorder(class, hwy, FUN = median), y = hwy)) +
  coord_flip()
```

```{r}
ggplot(data = mpg) +
  geom_boxploth(mapping = aes(y = reorder(class, hwy, FUN = median), x = hwy))
  
```

### 4 One problem with boxplots is that they were developed in an era of much smaller datasets and tend to display a prohibitively large number of “outlying values”. One approach to remedy this problem is the letter value plot. Install the lvplot package, and try using geom_lv() to display the distribution of price vs cut. What do you learn? How do you interpret the plots?

```{r}
install.packages("lvplot")
library("lvplot")
```
```{r}
install.packages("ggplot2")
library("ggplot2")
```

```{r}
ggplot(diamonds, aes(x = cut, y = price)) +
  geom_lv()
```

### 5 Compare and contrast geom_violin() with a facetted geom_histogram(), or a coloured geom_freqpoly(). What are the pros and cons of each method?

```{r}
ggplot(data = diamonds, mapping = aes(x = price)) + 
  geom_freqpoly(mapping = aes(colour = cut), binwidth = 500)
```

```{r}
ggplot(data = diamonds, mapping = aes(x = price)) +
  geom_histogram() +
  facet_wrap(~ cut, ncol = 1, scales = "free_y")
```


```{r}
ggplot(data = diamonds, mapping = aes(x = cut, y = price)) +
  geom_violin() +
  coord_flip()
```





### 6 If you have a small dataset, it’s sometimes useful to use geom_jitter() to see the relationship between a continuous and categorical variable. The ggbeeswarm package provides a number of methods similar to geom_jitter(). List them and briefly describe what each one does.
****
```{r}
install.packages("ggbeeswarm")
library("ggbeeswarm")
```

geom_quasirandom and geom_beeswarm

```{r}
ggplot(data = mpg) +
  geom_quasirandom(mapping = aes(x = reorder(class, hwy, FUN = median),
                                 y = hwy))
```

===============================

```{r}
diamonds %>% 
  count(color, cut) %>%  
  ggplot(mapping = aes(x = color, y = cut)) +
    geom_tile(mapping = aes(fill = n))
```

**d3heatmap or heatmaply packages**

##7.5.2.1 Exercises

### 1 How could you rescale the count dataset above to more clearly show the distribution of cut within colour, or colour within cut?

### 2 Use geom_tile() together with dplyr to explore how average flight delays vary by destination and month of year. What makes the plot difficult to read? How could you improve it?

```{r}
nycflights13::flights %>%
  group_by(month, dest) %>%
  summarise(dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(month), y = dest, fill = dep_delay)) +
  geom_tile() 
  
```


### 3 Why is it slightly better to use aes(x = color, y = cut) rather than aes(x = cut, y = color) in the example above?

use variables with the longer labels on y axis

7.5.3 Two continuous variables

```{r}
ggplot(data = diamonds) +
  geom_point(mapping = aes(x = carat, y = price))
```

```{r}
ggplot(data = diamonds) + 
  geom_point(mapping = aes(x = carat, y = price), alpha = 1 / 100)
```

```{r}
ggplot(data = diamonds) +
  geom_bin2d(mapping = aes(x = carat, y = price))
```
```{r}
ggplot(data = smaller) +
  geom_hex(mapping = aes(x = carat, y = price))
```
```{r}
ggplot(data = diamonds, mapping = aes(x = carat, y = price)) + 
  geom_boxplot(mapping = aes(group = cut_width(carat, 0.1)),varwidth = TRUE)
```
```{r}
ggplot(data = diamonds, mapping = aes(x = carat, y = price)) + 
  geom_boxplot(mapping = aes(group = cut_width(carat, 0.1)))
```
```{r}
ggplot(data = diamonds, mapping = aes(x = carat, y = price)) + 
  geom_boxplot(mapping = aes(group = cut_number(carat, 20)))
```

## 7.5.3.1 Exercises

### 1 Instead of summarising the conditional distribution with a boxplot, you could use a frequency polygon. What do you need to consider when using cut_width() vs cut_number()? How does that impact a visualisation of the 2d distribution of carat and price?

```{r}
ggplot(data = diamonds, 
       mapping = aes(x = price,
                     colour = cut_width(carat, 0.3))) +
  geom_freqpoly()
```
```{r}
ggplot(data = diamonds, 
       mapping = aes(x = price,
                     colour = cut_number(carat, 10))) +
  geom_freqpoly()
```


### 2 Visualise the distribution of carat, partitioned by price.

```{r}
ggplot(diamonds, aes(x = cut_number(price, 10), y = carat)) +
  geom_boxplot() +
  coord_flip()
```
```{r}
ggplot(diamonds, aes(x = cut_width(price, 2000, boundary = 0), y = carat)) +
  geom_boxplot(varwidth = TRUE) +
  coord_flip() 
```


### 3 How does the price distribution of very large diamonds compare to small diamonds. Is it as you expect, or does it surprise you?

 for a certain size, other factors such as cut, clarity, color play more of a role in the price.
 
### 4 Combine two of the techniques you’ve learned to visualise the combined distribution of cut, carat, and price.
```{r}
ggplot(diamonds, aes(x = cut_number(carat, 5), y = price, color = cut)) +
  geom_boxplot()
```
### 5 Two dimensional plots reveal outliers that are not visible in one dimensional plots. For example, some points in the plot below have an unusual combination of x and y values, which makes the points outliers even though their x and y values appear normal when examined separately.
Why is a scatterplot a better display than a binned plot for this case?
```{r}
ggplot(data = diamonds) +
  geom_point(mapping = aes(x = x, y = y)) +
  coord_cartesian(xlim = c(4, 11), ylim = c(4, 11))

```

unusual values will be binned normally~
